
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small }\\
    \end{tabular*}\vspace{-7pt}
    

}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Aviral Srivastava} \\ \vspace{1pt}
    Lucknow, Uttar Pradesh \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +91 9999999999 ~ \href{mailto:xxxx@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{xxxx@gmail.com}} ~
    \href{https://github.com/godofgeeks23}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/godofgeeks23}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KIET Group of Institutions}{Sept 2020 - Present}
      {Bachelor of Technology in Computer Science and Engineering (SGPA of 9.03)}{Ghaziabad, Uttar Pradesh, India}
  \resumeSubHeadingListEnd
  \vspace{-5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lucknow Public School}{2018 - 2019}
      {Senior Secondary (93.6\%)}{Lucknow, India}
  \resumeSubHeadingListEnd
  \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeSubheading
      {Lucknow Public School}{2016 - 2017}
      {Secondary (CGPA of 10.0)}{Lucknow, India}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cyethack Solutions }{Sept 2022 -- Present}
      {Product Developer Intern}{Online}
      \resumeItemListStart
        \resumeItem{Created a web based backend + frontend tool (using MERN stack) to interact, and see all the information related to the Web reconnaissance. }
    \resumeItemListEnd
    
    \resumeSubheading
      {C3i Hub, Indian Institute of Technology, Kanpur }{July 2022 -- Oct 2022}
      {Summer Security Research Intern}{Kanpur, India}
      \resumeItemListStart
        \resumeItem{Set up the server with Elasticsearch, Kibana and Logstash, and set up Apache Kafka to be used with Logstash. }
        \resumeItem{Scraped tweets based on keywords, identified sources and real time from twitter (using tweepy). Also collected data from telegram using telethon - fetched live messages, implemented filtering based on keywords, channel search, extracting channel users info.}
        \resumeItem{Analysis of the collected information related to recognized illegal content using Natural Language Processing. }
        \resumeItem{Maintained project documentation and the GitHub repository. }
    \resumeItemListEnd
    
    \resumeSubheading
      {GirlScript Foundation}{Apr 2022 -- July 2022}
      {Organiser, Web3 Camp}{Online}
      \resumeItemListStart
        \resumeItem{Successfully managed and conducted the Web3 camp for Kanpur region, with over 200+ registrations.}
    \resumeItemListEnd
    
    \resumeSubheading
      {GirlScript Foundation}{ Dec 2021 -- March 2022}
      {Campus Ambassador, Summer of Code}{Online}
      \resumeItemListStart
        \resumeItem{Spread awareness about Open Source among the students.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Ek Prayas}{ Dec 2021 -- Present}
      {Coordinator}{Ghaziabad, India}
      \resumeItemListStart
        \resumeItem{Ek Prayas is a social welfare club aimed towards spreading awareness about and eradication of smoking/drinking/drugs used by youth.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Py-LMDC} $|$ \emph{Python} $|$ {github.com/godofgeeks23/python-LMDC}}{temp}
          \resumeItemListStart
            \resumeItem{A ML based Linux Malware Detection and Classification
System built using Python.}
          \resumeItemListEnd
    \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Twitter Data Miner} $|$ \emph{Python, Elasticsearch, Kibana, Logstash}  $|$ {github.com/godofgeeks23/twitter-data-miner}}{temp}
          \resumeItemListStart
            \resumeItem{A tool to scrape live Twitter data using Python and analyzing it using Elastic stack.}
          \resumeItemListEnd
    \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Spider} $|$ \emph{Python, SQL}  $|$ {github.com/godofgeeks23/Spider}}{temp}
          \resumeItemListStart
            \resumeItem{A high performance webcrawler, developed in python.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%
%-----------Achievements-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeItemListStart
        \resumeItem{Got an \textbf{internship offer} from \textbf{Airtel} for \textbf{Security intern} role.}
        \resumeItem{Secured \textbf{2nd Rank} in AlanAI Hacks '22 Hackathon.}
        \resumeItem{Secured a place among HCL-IITK 2021 \textbf{Finalists} (in \textbf{top 0.00092\%} teams.)}
        \resumeItem{\textbf{Finalists (top 5)} of Shaastra Web Crawler Hackathon - IIT Madras.}
        \resumeItem{\textbf{Won} the Begig HacXmas Hackathon, 2022.}
        \resumeItem{\textbf{Finalist} of the Egnite Ideathon '22.}
        \resumeItem{Involved in student developer communities like \textbf{MLH (Major League Hacking)} and \textbf{Community Classroom}.}
      \resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}
 
 %
%-----------Profile Links-----------
\section{Profile Links}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \resumeItemListStart
        \resumeItem {\href{https://github.com/godofgeeks23}{GitHub}}
        \resumeItem {\href{https://twitter.com/godofgeeks_}{Twitter}}
        \resumeItem {\href{https://www.linkedin.com/in/aviral-srivastava-07b1a4202/}{LinkedIn}}
      \resumeItemListEnd
 \end{itemize}
 \vspace{-16pt}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, JavaScript, Java, HTML/CSS, Bash, Go, SQL} \\
     \textbf{Frameworks}{: Express, React, Node, MongoDB, Elasticsearch, BootStrap, TailWind, Kibana, Logstash } \\
     \textbf{Developer Tools}{: Git, Linux, Visual Studio Code, Figma} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, OpenCV} \\
     \textbf{Theoretical Concepts}{: Data Structures and Algorithms, DMBS, Operating System} \\
    }}
 \end{itemize}
 \vspace{-16pt}

%
%-----------Miscellaneous-----------
\section{Miscellaneous}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Consider myself to be a \textbf{teamworker}.} \\
     {Proficient in English and Hindi.} \\
     {\textbf{Hobbies:} Solving CTFs, Sketching, Cooking.} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}


